---
title: "A to ZEV"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prop 30: A Closer Look Taxing Millionaires for EVs {.tabset}

### Funding

The following map shows how many millionaires would be taxed under this proposition & the subsequent income that would be raised in 2020 USD.

```{r echo = FALSE, results = FALSE, warning = FALSE,message =-FALSE}
source("income_map.R")
```

```{r echo = FALSE, message = FALSE}
m
```

**How do we calculate these numbers?**

The [American Community Survey](https://www.census.gov/programs-surveys/acs) reports how many people make over \$200,000 annually by where they live. Using information from California's tax board, we can distribute the total number of people making over \$2 million annually in the state & the amount of money they would pay proportionally to each community based on the percent of people making over \$200,000.

### EV Infrastructure {.tabset}

#### Chargers Now

#### Future Possibilities